intro

### 2022-08-05 06_Paper/ER-ED/ERED_Stage1/Manuscript_ERED_Stage1.tex
renamed directories

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 6289}
\usepackage{lineno}

@@

In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{34}).

@@

To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{67}.
First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) will be applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors will be specified.
\[
\begin{split}
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
\end{split}
\]
Level-1-predictors will be centered within cluster\textsuperscript{68}.
Residuals of the final model will be inspected visually.
Intraclass correlation coefficient (ICC), \(\rho\), will be reported for each model (null model, as well as full model).

@@

\leavevmode\vadjust pre{\hypertarget{ref-Zerna2022}{}}%
\CSLLeftMargin{34. }%
\CSLRightInline{Zerna, J., Scheffel, C., Kührt, C. \& Strobel, A. When easy is not preferred: An effort discounting for estimating subjective values of taks. \emph{PsyArXiv} (2022) doi:\href{https://doi.org/10.31234/osf.io/ysh3q}{10.31234/osf.io/ysh3q}.}

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 6303}
\usepackage{lineno}

@@

In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna, Scheffel et al.\textsuperscript{34}).

@@

To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{67}.
First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) will be applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors will be specified.
\[
\begin{split}
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
\end{split}
\]
Level-1-predictors will be centered within cluster\textsuperscript{68}.
Residuals of the final model will be inspected visually.
Intraclass correlation coefficient (ICC), \(\rho\), will be reported for each model (null model, as well as full model).
The presented MLM follows the conceptualization of Zerna, Scheffel, et al.\textsuperscript{34}

@@

\leavevmode\vadjust pre{\hypertarget{ref-ZernaScheffel2022}{}}%
\CSLLeftMargin{34. }%
\CSLRightInline{Zerna, J., Scheffel, C., Kührt, C. \& Strobel, A. When easy is not preferred: An effort discounting for estimating subjective values of taks. \emph{PsyArXiv} (2022) doi:\href{https://doi.org/10.31234/osf.io/ysh3q}{10.31234/osf.io/ysh3q}.}

### 2022-08-05 06_Paper/ER-ED/ERED_Stage1/Stage1_revision/TheoreticalBackground_rev.Rmd
renamed directories

The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] to regulate emotions is an important cognitive skill. 
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning[@Gross1998emerging].
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification[@Gross1998antecedent], and, following the taxonomy of Powers and LaBar[-@Powers2019], individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process[@Gross1998antecedent].
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy[@Gross1998antecedent].
This postulated temporal sequence of ER strategies influences their effectiveness.
Albeit it is meta-analytically proven that all mentioned strategies reduce subjective emotional experience, distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed only small to medium effect sizes (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
In contrast, distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45[@Webb2012].

>>>>

The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] is an important cognitive skill. 
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning[@Gross1998emerging].
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification[@Gross1998antecedent], and, following the taxonomy of Powers and LaBar[-@Powers2019], individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process[@Gross1998antecedent].
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy[@Gross1998antecedent].
This postulated temporal sequence of ER strategies influences their effectiveness.
Albeit it is meta-analytically proven that all mentioned strategies reduce subjective emotional experience, distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed only small to medium effect sizes (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
In contrast, distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45[@Webb2012].

### 2022-08-05 06_Paper/ER-ED/ERED_Stage2/TheoreticalBackground.Rmd
renamed directories

In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al.[@Zerna2022]).

>>>>

In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna, Scheffel et al.[@ZernaScheffel2022]).
